Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-25 Paper/Paper.tex
conclusion slightly improved

The main future direction is larger scales. This implies $3$ improvements.
First, gather more songs from the Echo Nest API. Second, efficiently work
with larger codebooks. Some improvements have been published for $k$-means
that avoid comparing every code to every sample. Initialization
should also be modified, so every codeword is used (unlike in
Figure \ref{fig:freqs}). Third, the learning
algorithm must not converge too fast. We could add a filter that selects
increasingly hard example to encode, or merge many codebooks in a similar
fashion as hierarchical Gaussian mixtures \cite{Vasconcelos2001}.

>>>>

For even larger scales, we will focus on three facets.
First, gather more songs from the Echo Nest API. 
%
Second,
larger codebooks paired with computationally efficient algorithms.
Improvements to $k$-means
avoid comparing every code to every new sample. Initialization
should also be modified, so every codeword is used (unlike in
Figure \ref{fig:freqs}). 
%
Third, the learning
algorithm must not converge too fast. We could add a filter that selects
increasingly difficult examples to encode, or merge many codebooks in a 
similar fashion as hierarchical Gaussian mixtures \cite{Vasconcelos2001}.
